---
title: "Getting started with dieroller"
author: "Bartell lin"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, echo=FALSE, include = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
library("dieroller")
```

##Die Rolling

The package `"Dieroller"` is an implementation for simulating rolling a die a given number of times, and to
visualize the relative frequencies in a series of such die rolls.


##Creating a `die`

The first step is to create a `"die"` object with the function `die()`:

```{r}
fair <- die()
fair
```

By default, the function creates a die with sides 1-6, each with probablility 1/6.

##Rolling

You can roll the die with the `roll()` function:

```{r}
fair_roll <- roll(fair, 50)
fair_roll
```

##Plotting

You can plot the rolls as well:

```{r}
plot(fair_roll)
```


##Summary

You can even view a summary of the rolls:

```{r}
summary(fair_roll)

```
